### 2013-04-05 MSteenhagen-CV.tex
Fixed hyphen
Swapped memberships around
Added Birkbeck worskhop presentation
Slight modification of dissertation description
Minor change in appointment description

\ind Dissertation research on the nature of human experience of pictorial representation. Supervisor: Prof. Mark Eli Kalderon.

@@

\ind 2009--Present. Tutorial Assistant in Philosophy and Psychology\\ (Psychoanalysis, Metaethics, Perception \& epistemology, Descartes).

@@

\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks (recent)}
\medskip
\ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% 
% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip
\marginhead{Professional organisations}
\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}

@@

@@

\ind 2007-2009. Editor of \href{http://www.cimedart.nl}{\emph{Cimedart}}, Philosophy Journal of the University of Amsterdam.

>>>>

\ind Dissertation on the nature of human experience of pictorial representation. Supervisor: Prof. Mark Eli Kalderon.

@@

\ind 2009--Present. Tutorial Assistant in Philosophy\\ (Psychoanalysis, Metaethics, Perception \& epistemology, Descartes).

@@

\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks (recent)}
\medskip
\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

\ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% 
% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip
\marginhead{Professional organisations}

@@

\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}

@@

\ind 2007--2009. Editor of \href{http://www.cimedart.nl}{\emph{Cimedart}}, Philosophy Journal of the University of Amsterdam.
